

% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=9in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}


\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{
Compass Lexecon \\
630 Fifth Avenue\\
Suite 2600\\
New York, NY 10111\\
 }
 
\begin{center}
\large \bf{Andrew S. Winterman} \end{center}
\medskip\hrule height 1pt
\begin{center}
3811 SE Ellis \\ Portland, OR 97202 \\ (714) 362 6823
\end{center}  

%email: "jobs@steckconsulting.com"
%subject: "Data Analyst/Programmer 201012"


\opening{Dear Dr. Saha} 
 
 I am applying for a research analyst position at Compass Lexecon on the recommendation of an employee at the Chicago office, Swaroop Poudel, a fellow Reed College alumnus. I would like this application to be considered by following offices, listed in order of preference: New York; Oakland; Washington, D.C.
  
I have experience applying statistics in a behavioral genetics laboratory under the direction of professors Susan C. P. Renn and Albyn Jones. In my research with them, I solved applied problems having to do with interpretation of data using $R$, a language new to me at the time. I found the work satisfying, so much so that my last subject of study at the laboratory evolved naturally into my senior thesis. A position at Compass Lexecon would be an opportunity for me to do more computational statistics, further hone my programming skills, and gain a more intimate knowledge of the tools used for the interpretation and management of large data sets. I want to join Compass Lexecon so that I might continue to bring sense to data. 
 
 I like detail oriented work, especially when it involves writing code. I have a good understanding of the careful patience required to do mathematics correctly, whether abstract or applied. I have strong social skills, as evidenced by my four years as a member of the Reed College ultimate frisbee team and a recent volunteer position as an outdoor trip student leader. I am sharp and calm, a goal-oriented team player. These skills and characteristics make me a good choice for a position at Compass Lexecon. I would appreciate the opportunity to further discuss my background and the analyst position with you, either over the phone.  I can be reached by phone at (714) 362 6823 or by email at andywinterman@gmail.com. 

Thank you for reviewing my application.

Sincerely, \\
Andrew Winterman
\encl{Resume; references; unofficial transcript; letter on grades at Reed; writing sample.}  				% Enclosures

P.S. Official print transcript available upon request.
\end{letter}
 

\end{document}







%\documentclass[12pt, letterpaper, oneside]{letter}



% \begin{document}

I am applying for a position at the Analysis Group.


I have experience using R (an environment for statistical computing relying on the language, S), LaTeX, Java and Haskell. My current projects include working through the problems presented by Project Euler (http://projecteuler.net/) using lisp, learning Unix, html, and gaining a more technical understanding of the internet so as to make myself more marketable to employers in the field of computer science. 




%\end{document}