

% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=9in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}


\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{
The Analysis Group \\
San Francisco \\
650 California Street \\
Floor 23\\
San Francisco, CA  94108} 

\begin{center}
\large \bf{Andrew S. Winterman} \end{center}
\medskip\hrule height 1pt
\begin{center}
3811 SE Ellis \\ Portland, OR 97202 \\ (714) 362 6823
\end{center} 


 
\opening{To whom it may concern:} 
 
\noindent I am applying for the position of analyst at the Analysis Group. I am motivated by a presentation given  by several Analysis Group employees at Reed College in September.  % Despite some differences, %(researching as part of a team, meeting tougher deadlines, the real-world consequences of the research, etc.)
 I could not resist comparing the work they described to writing a thesis. In both one must placate an expert academic, explore a little-known topic, write carefully for a non-specialist audience, and do rigorous mathematics. Having completed my thesis, I am cheered by the prospect of doing such work for pay.
 
 \noindent I found writing a thesis in statistics enjoyable, despite the stress culture associated with the process at Reed College. I justified everything I believed to be true about statistical tests of equivalence, and I may even have found - pending additional research - a new result. Despite changing topics after the first semester, I was able to write the fifty page document in the three months of the second semester of my senior year, sleeping well, eating well, and exercising regularly all the while. 
 
\noindent My thesis experience demonstrates an independence, balance and appetite for knowledge appropriate to an analyst at the Analysis Group.  I like detail oriented work, especially when it involves writing code. I have a good understanding of the careful patience required to do mathematics correctly, whether abstract or applied. Finally, I have strong social skills, as evidenced by my four years as a member of the Reed College ultimate frisbee team and a recent volunteer position as an outdoor trip student leader. I am sharp and calm, a goal-oriented team player. These skills and characteristics make me a good choice for the position of analyst at the Analysis Group. I would appreciate the opportunity to further discuss my background with you, either over the phone or in person. I can be reached by phone at (714) 362 6823 or by email at andywinterman@gmail.com. %Should I mention that I have family in the bay area, making travelling their affordable?

Thank you for reviewing my application.

Sincerely, \\
Andrew Winterman
\encl{Resume, Unofficial Transcript, and Letter on Grades at Reed}  				% Enclosures

\end{letter}
 

\end{document}







%\documentclass[12pt, letterpaper, oneside]{letter}



% \begin{document}

I am applying for a position at the Analysis Group.


I have experience using R (an environment for statistical computing relying on the language, S), LaTeX, Java and Haskell. My current projects include working through the problems presented by Project Euler (http://projecteuler.net/) using lisp, learning Unix, html, and gaining a more technical understanding of the internet so as to make myself more marketable to employers in the field of computer science. 




%\end{document}