


% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=9in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}


\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{
Stumptown Coffee\\
3356 SE Belmont St.\
Portland, OR 97214\\}

\begin{center}
\large \bf{Andrew S. Winterman} \end{center}
\medskip\hrule height 1pt
\begin{center}
3811 SE Ellis \\ Portland, OR 97202 \\ (714) 362 6823
\end{center}  

\opening{Dear Bob,} 
 
 I am applying for a Barrista position at the Stumptown Coffee. Since moving to Portland a few years ago for college, I have become an avid coffee drinker. A recent graduate, I want to spend the foreseeable future making amazing coffee before applying to graduate school. In my opinion, Stumptown is the best place to do so. 

I like to brew thick flavorful coffee| I use a french press and sometimes a Bialleti, but my favorite method by far is Turkish style coffee. I drink espresso. I know how it should taste, and although I do not have my own machine, I have pulled a few shots at the Reed College coffee shop-- the Paradox. 

 I am detail oriented, calm and patient. I take pride in whatever I make, whether the media be wood, the written word, food or coffee. I have strong social skills, as evidenced by my four years as a member of the Reed College ultimate frisbee team and a recent volunteer position as an outdoor trip student leader. I love to take the initiative. I am sharp and clean, a goal-oriented team player. These skills and characteristics make me a good choice for the Barrista position. I would appreciate the opportunity to further discuss my background and the position with you, either over the phone or in person. I can be reached by phone at (714) 362 6823 or by email at andywinterman@gmail.com. 

Thank you for reviewing my application.

Sincerely, \\
Andrew Winterman
\encl{Resume}
				% Enclosures

\end{letter}
 

\end{document}







%\documentclass[12pt, letterpaper, oneside]{letter}



% \begin{document}

I am applying for a position at the Analysis Group.


I have experience using R (an environment for statistical computing relying on the language, S), LaTeX, Java and Haskell. My current projects include working through the problems presented by Project Euler (http://projecteuler.net/) using lisp, learning Unix, html, and gaining a more technical understanding of the internet so as to make myself more marketable to employers in the field of computer science. 




%\end{document}
