\documentclass[11pt]{letter}

\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\usepackage{fancyhdr}
%\usepackage[document]{ragged2e}
\usepackage[german]{babel}
\usepackage[top=1in, bottom=1in, right=1in, left=1in, footskip=16pt]{geometry}

%\usepackage[compact]{titlesec}
\usepackage{changepage}


\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{soul}


\pagestyle{fancy}

\fancyhead{}

\renewcommand{\headrulewidth}{1pt}

\usepackage{hyperref}
\hypersetup{
            colorlinks=true,
            urlcolor=steelblue,
            linkcolor=steelblue
}

\usepackage{color}
\definecolor{steelblue}{rgb}{0.02638, 0.5, 0.67578125}

\date{}
\chead{
    \textsc{\huge{\so{andrew winterman}}}
}
\cfoot{ 
    \hrule  \\
    \vspace{3px}
    2807 NE Glisan Apt. 304, Portland, OR 97232 \\
andywinterman@gmail.com - 714 362 6823 - 
\url{https://github.com/AWinterman}
}


\begin{document}


\begin{letter}{Urban Airship \\
334 NW 11th Ave. \hfill \today \\
Portland, OR 97209\\ 
}
\address{}

\begin{adjustwidth}{1in}{1in}

    \opening{To whom it may concern:}

    \thispagestyle{fancy}
I am applying for the Core Data Engineer position at Urban Airship on the
strength of my past experience and the recommendation of Dan Colish, a fellow
member of the Portland Python User's Group. I am excited by this opportunity to
employ predictive statistics and machine learning in the context of push
notification management.

I have experience at a boutique web development company prototyping data
visualization methods, doing data analysis, and implementing machine learning
algorithms for social media data. I do the full process, from data retrieval to
processing to constructing working prototypes of visualizations. I make scale
models of the finely polished product we push out the door. My data has, for
the most part, been small enough for my aging IMac to handle it, but I have run
large computations on Amazon's Elastic Cloud Compute, and written map-reduce
jobs for the Elastic MapReduce web service.

I am detail oriented, patient, and a quick study.  Although I do not currently
speak Java, I have a history of picking up new languages quickly, whether they
are natural or computer languages.  Sharp and calm, I am a goal-oriented team
player, eager to contribute. I look forward to discussing my background and the
Core Data Engineer position at Urban Airship, either over the phone or in
person.

\closing{
Thank you, \\
Andrew Winterman}


\end{adjustwidth}


\end{letter}


\end{document}
