

% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:

\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=9in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
\begin{letter}{Periscopic \\
1314 NW Irving St. \textsc{no}. 214 \\
Portland, OR 97209\\ 
}
\begin{center}
\large \bf{Andrew S. Winterman} 
\end{center}
\medskip\hrule height 1pt
\begin{center}
3811 SE Ellis \\ Portland, OR 97202 \\ (714) 362 6823
\end{center}  
\opening{Dear Ms. Rees:} 

I am interested in Periscopic because I am excited about data
visualization. Visualizations have the potential to render data
engaging to a diverse audience, encouraging a scientific,
rationalist world view. They promise intellectual
advancement| the more people that engage with a problem, the more
likely one of them is to solve it. Finally, they look like fun to make. I am especially heartened by the
motto on Periscopic's website: ``Socially responsible information
visualization: Doing good with data.''  I am excited to apply myself
towards making ours a more data driven, rational society.

I have experience programming in a behavioral genetics laboratory at
Reed College under the direction of Professors Susan C. P. Renn and
Albyn Jones. In my research with them, I solved applied problems
having to do with the interpretation of data using $R$, a computer
language new to me at the time. I found the work satisfying, so much
so that my last subject of study at the laboratory evolved naturally
into my senior thesis in statistics. Since graduating in December, I
have been pursuing computer science and programming (using  the
computer languages Haskell and Scala), auditing courses at Reed and learning
about the \textsc{unix} operating system.
 
I am detail oriented, patient, and, because of my rigorous education,
accustomed to tackling multiple projects simultaneously. I have strong
social skills, as evidenced by my four years as a member of the Reed
College ultimate frisbee team and a recent volunteer position as an
outdoor trip student leader. Sharp and calm, I am a goal-oriented, team
player. I would appreciate the opportunity to discuss my
background and a position at Periscopic  with you, either over the phone or in
person. I can be reached by phone at (714) 362 6823 or by email at
andywinterman@gmail.com.

Thank you for reviewing my application.

Sincerely, \\
Andrew Winterman
\encl{Resume; unofficial transcript}
				% Enclosures
\end{letter}
 

\end{document}







%\documentclass[12pt, letterpaper, oneside]{letter}



% \begin{document}

I am applying for a position at the Analysis Group.


I have experience using R (an environment for statistical computing relying on the language, S), LaTeX, Java and Haskell. My current projects include working through the problems presented by Project Euler (http://projecteuler.net/) using lisp, learning Unix, html, and gaining a more technical understanding of the internet so as to make myself more marketable to employers in the field of computer science. 




%\end{document}