

% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:

\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=9in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}


\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\opening{Ms. Peele:} 


\begin{letter}{
Internship Position\\
Renewable Northwest Project \\
917 SW Oak,
Suite 303 \\
Portland, OR 97205 \\ }

\begin{center}
\large \bf{Andrew S. Winterman} \end{center}
\medskip\hrule height 1pt
\begin{center}
3811 SE Ellis \\ Portland, OR 97202 \\ (714) 362 6823
\end{center}  

%email: "jobs@steckconsulting.com"
%subject: "Data Analyst/Programmer 201012"



I am applying for an internship position at %NAME OF FIRM!!!
the Renewable Northwest Project.  I would like to analyze the economic
impact of the wind and solar energy industries in the Pacific
Northwest. This project pertains not just to the firms that
market and produce green energy, but to the Northwest community as a
whole. A report on the green energy industry's contribution to labor
and output is useful in informing state and federal fiscal policy and
regulation of the energy sector, especially in light of the fiscal
tightening our large budget deficits must eventually precipitate. This
internship provides an opportunity to place my data gathering and
analysis skills on the right side of the debate: at the service of an
industry with a positive impact on our society.
 
I have experience programming in a behavioral genetics laboratory at
Reed College under the direction of professors Susan C. P. Renn and
Albyn Jones. In my research with them, I solved applied problems
having to do with the interpretation of data using $R$, a computer
language new to me at the time. I found the work satisfying, so much
so that my last subject of study at the laboratory evolved naturally
into my senior thesis in statistics. Since graduating in December, I
have been pursuing computer science and programming (using  the
computer languages Haskell and Scala)| auditing courses and learning
about the Unix operating system.
 
I am detail oriented, patient, and, because of my rigorous education,
accustomed to tackling multiple projects simultaneously. I have strong
social skills, as evidenced by my four years as a member of the Reed
College ultimate frisbee team and a recent volunteer position as an
outdoor trip student leader. I am sharp and calm: a goal-oriented, team
player. These skills and characteristics make me a good choice for the
internship position at %FIRMS NAME
RNP. I would appreciate the opportunity to further discuss my
background and the position with you, either over the phone or in
person. I can be reached by phone at (714) 362 6823 or by email at
andywinterman@gmail.com.

Thank you for reviewing my application.

Sincerely, \\
Andrew Winterman
\encl{Resume, writing sample}
				% Enclosures

\end{letter}
 

\end{document}







%\documentclass[12pt, letterpaper, oneside]{letter}



% \begin{document}

I am applying for a position at the Analysis Group.


I have experience using R (an environment for statistical computing relying on the language, S), LaTeX, Java and Haskell. My current projects include working through the problems presented by Project Euler (http://projecteuler.net/) using lisp, learning Unix, html, and gaining a more technical understanding of the internet so as to make myself more marketable to employers in the field of computer science. 




%\end{document}