\message{ !name(CoverLetter.tex)}

% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:

\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=9in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\message{ !name(CoverLetter.tex) !offset(-3) }



\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\opening{Bill Livek:} 


\begin{letter}{
Rentrack Corporation\\
7700 NE Ambassador Place, 3rd Floor\\
Portland, OR 97220-1393}

\begin{center}
\large \bf{Andrew S. Winterman} \end{center}
\medskip\hrule height 1pt
\begin{center}
3811 SE Ellis \\ Portland, OR 97202 \\ (714) 362 6823
\end{center}  

%email: "jobs@steckconsulting.com"
%subject: "Data Analyst/Programmer 201012"



I am applying for the statistical research analyst position at %NAME OF FIRM!!!
Rentrack. I am motivated to apply by my affinity for statistical
research. I take great satisfaction in coaxing sense from data. Why?
Because it feels like a real, meaningful contribution to the state of
human knowledge. Gathering data is itself difficult and subtle. It's
interpretation is a crucial step. Communic
 
I have experience programming in a behavioral genetics laboratory at
Reed College under the direction of professors Susan C. P. Renn and
Albyn Jones. In my research with them, I solved applied problems
having to do with the interpretation of data using 
\message{ !name(CoverLetter.tex) !offset(24) }

\end{document}







%\documentclass[12pt, letterpaper, oneside]{letter}



% \begin{document}

I am applying for a position at the Analysis Group.


I have experience using R (an environment for statistical computing relying on the language, S), LaTeX, Java and Haskell. My current projects include working through the problems presented by Project Euler (http://projecteuler.net/) using lisp, learning Unix, html, and gaining a more technical understanding of the internet so as to make myself more marketable to employers in the field of computer science. 




%\end{document}