%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin,line]{resume}
\usepackage[german]{babel}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Andrew Winterman}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}


    3811 SE Ellis,                           \hfill  mobile: (714) 362-6823          \vspace{0mm}\\\vspace{0mm}%
    Portland, OR 97202                         \hfill     e-mail: andywinterman@gmail.com      \vspace{0mm}\\%
  \vspace{-4.5mm}%

    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Summary}

Reed mathematics major looking for post-graduation employment in statistics, scientific computation, or programming.


\section{\mysidestyle Publications}
Winterman, A. (2010) \textit{Statistical Tests of Equivalence}. Unpublished Undergraduate Thesis, Reed College, Portland OR. \\
\vspace{-2mm} \\
 N. M. Murari, R. Thomas, A. Winterman, R. E. Melgarejo, S. P. Pavunny, and R. S. Katiyar. ``Structural, electrical, and magnetic properties of chemical solution deposited Bi(Fe$_{0.95}$Cr$_{0.05}$)O$_3$ thin films on platinized silicon substrates," J. Appl Physics 105, 084110 (2009).     %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
\textbf{Reed College}: B.A. in Mathematics; Thesis in statistics.
 \vspace{1mm} \hfill Aug 2006 - Dec 2010 \vspace{1mm}\\
\textbf{Deutsche Sommerschule am Pazifik}:  Language Immersion (German) \vspace{1mm} \hfill Summer 2009
\vspace{1mm} \\
\textbf{Universidad Belgrano}: Language Immersion (Spanish) \vspace{1mm} \hfill Summer 2006 \vspace{1mm}


    % Employment History
    \section{\mysidestyle Scientific\\Employment} 
\textbf{Research Experience for Undergraduates} \hfill  Intern \\ 
\textbf{at Reed College} \ \  \hfill Summer 2010 \\
Repaired and improved available statistical tools for cDNA microarray analysis. Worked with a team of undergraduates under Professors Susan Renn and Albyn Jones, developed statistical test of equivalence for use with microarray day. \\
\vspace{-2mm} \\
%\textbf{ Internal Research Grant} \hfill Assistant  \\ 
%\textbf{Reed College} \hfill Summer 2009 \vspace{0mm}	\\
%Researched combinatorics with Prof. V. Rao Potluri.
%\\\vspace{-2mm}\\
\textbf{Researcher at University of Puerto Rico,} \hfill  Intern\\
\textbf{Rio Piedras, Spectrum Laboratories} \hfill Fall 2008	\\
Executed a complicated scientific procedure to exacting standards. Coauthor on paper N. M. Murari et al (2009), full citation below.
\\\vspace{-2mm}\\
\textbf{Westf"alische Wilhelms-Universit"at M"unster and the} \hfill  Intern \\
\textbf{German Academic Exchange Service (DAAD)} \hfill Summer 2008	\\
Operated a tomographic atom probe, transmission electron microscope, and a field ion microscope. \\ Executed delicate scientific procedure designed to test the effect of extreme temperatures on the rate of diffusion of nano-materials.

\section{\mysidestyle Student Organizations }

\textbf{Outdoor Odyssey} \hfill Student Leader \\
\textbf{Orientation Trip} \hfill Summer 2010 \\
Lead four day backpack in Mt. Adams wilderness area for incoming Reed College freshmen. Responsibilities include group safety, organizing meals, clean water, tending group moral.
\\\vspace{-2mm}\\
\textbf{Jump Rope} \hfill Organizer
\\\textbf{Club}  \hfill Spring 2009\\
Student Health: Installed jump ropes in lobby of Reed College library to combat stress culture, encourage students to exercise as a study break. 

\section{\mysidestyle Language \& Construction \\ Employment}
\textbf{VOZ Workers' Rights}  \hfill Volunteer \\ \textbf{Education Project} \hfill Fall 2009 \\ Taught English to Latin American adult day laborers while they waited for employment. \\
\vspace{-2mm}\\    
\textbf{Ayuda} \hfill Volunteer \\    
\textbf{Directa} \hfill Summer 2007	\\
Constructed ``dust free" building in remote Andean village to properly house government issued computers. Tutored more advanced Quechua students in English vocabulary and grammar.    


%_________________________________________________________________________________________________________________
\newpage

    % Programming
    \section{\mysidestyle Computer\\Skills}
 R: A language and environment for statistical computing, \LaTeXe, \\ Haskell, Wolfram's Mathematica, Java, HTML.
    %__________________________________________________________________________________________________________________
    % T
    \section{\mysidestyle Languages}
English (Fluent) \\
Spanish (Advanced)\\
German (Intermediate)   %__________________________________________________________________________________________________________________
    % Interests
    \section{\mysidestyle Interests} 

Ultimate Frisbee (member of college team, 2006 - 2010) \\
Cooking (Japenese, Italian, preferably for large groups) \\
Tango \& Jazz, Commuting by bike \\
Traveling, Piano \& Percussion 

\section{\mysidestyle Relevant Coursework}
Mathematics 331: Linear Algebra \\
Mathematics 391: Probability \\
Mathematics 392: Mathematical Statistics \\
Economics 201: Introduction to Economic Analysis \\
Economics 342: International Macroeconomics \\



%__________________________________________________________________________________________________________________



    %__________________________________________________________________________________________________________________
    % Referees
%    \section{\mysidestyle Referees} 
%    {\sl Available on request.}



%______________________________________________________________________________________________________________________
%\section{\mysidestyle Referees} 

%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Professor Kuldip Paliwal}       &  \textbf{Dr Stephen So}                   \\
%Professor                               &  Associate Lecturer                       \\
%Griffith University                     &  Griffith University                      \\
%Nathan, Queensland, Australia           &  Gold Coast, Queensland, Australia        \\
%phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
%e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
%\end{tabular}

%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Dr Conrad Sanderson}            &  \textbf{Mr Sean Loye}                    \\
%Researcher                              &  Systems Engineer                         \\
%National ICT Australia                  &  Hewlett Packard                          \\
%St Lucia, Queensland, Australia         &  Milton, Queensland, Australia            \\
%phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
%e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
%\end{tabular}



%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

