\documentclass[11pt]{article}
\setlength{\tabcolsep}{4pt}
\setlength{\parindent}{0cm}
\setlength{\voffset}{0cm}
\setlength{\headsep}{15pt}
\setlength{\footskip}{-25pt}
%\pagestyle{empty}

\renewcommand{\arraystretch}{1}
\newcommand{\fbuff}{\vfill}
\newcommand{\buff}{\vspace{4px}}

\newcommand{\Entry}[5]{
    \begin{tabular}{p{0.01\textwidth}p{0.15\textwidth}p{0.7\textwidth}p{0.12\textwidth}}  
        & \scshape{#1} \newline \slshape{#2} & #3 & #4\newline#5 \\
\end{tabular}
}

%\newcommand{\MySection}[1]{
%
%    \vspace{-22pt}
%    \begin{tabular}{p{0.15\textwidth}p{0.68\textwidth}p{0.1\textwidth}}  
%    &
%    \begin{flushleft}\textcolor{steelblue}{\large{\textbf{\textsc{#1}}}}\end{flushleft} &  \\ 
%    \end{tabular}
%    \vspace{-14pt}
%}

\newcommand{\MySection}[1]{
    %\vspace{-22pt}
     \begin{tabular}{p{0.15\textwidth}p{0.68\textwidth}p{0.1\textwidth}}  
        \multicolumn{3}{l}{\large{\textbf{#1}}} 
    \end{tabular}
    %\vspace{-14pt}

}
\usepackage{fancyhdr}
\usepackage[document]{ragged2e}
\usepackage[german]{babel}
\usepackage[top=1in, bottom=1in, right=1in, left=1in, footskip=16pt]{geometry}

\usepackage{color}
\definecolor{steelblue}{rgb}{0.02638, 0.5, 0.67578125}
\usepackage[compact]{titlesec}
\usepackage{multirow}
\usepackage{array}
\usepackage{hyperref}
\hypersetup{
            colorlinks=true,
            urlcolor=steelblue,
            linkcolor=steelblue
}


\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{soul}


\pagestyle{fancy}

\fancyhead{}

\renewcommand{\headrulewidth}{1pt}
\chead{
    \textsc{\huge{\so{andrew winterman}}}
}
\cfoot{ 
    \hrule  \\
    \vspace{3px}
    2807 NE Glisan Apt. 304, Portland, OR 97232 \\
andywinterman@gmail.com - 714 362 6823 - 
\url{https://github.com/AWinterman}
}

\begin{document}
\hspace{0.175\textwidth}\parbox{0.69\textwidth}{
 Critical, creative thinker, quick learner, disciplined, numerate. \\ 
 \textit{Education}: Reed College (2010) Mathematics BA,
\href{https://github.com/AWinterman/Thesis/blob/master/TestofEquivalence.pdf?raw=true}{Thesis}. \\
    \textit{Specialties}:  \normalfont Data Visualization, Machine Learning,
Statistics. \newline
}
\buff
\fbuff

\MySection{Employment History}
\buff
\Entry{data \newline scientist}{\href{http://www.periscopic.com/}{Periscopic}}{Translate data into graphics for
    intuitive interpretation. Implement software for machine learning, data analysis.
    Research new projects, make sense of data from diverse sources (economics,
    ecology, epidemiology, technology, etc.). Prototype visualization
    methods uniquely suited to the data set and to the needs of the client.
}{Aug 2011}{Present}

\buff
\Entry{\href{http://www.nsf.gov/funding/pgm_summ.jsp?pims_id=5517&from=fund}{reu} intern}{Reed College}{Repaired and improved available
statistical tools for cDNA microarray analysis using the R programming
language. Collaborated with a team of undergraduates under Professors Renn and Jones. }{May 2010}{Aug 2010}

\buff

\Entry{Researcher}{University of Puerto Rico}{Investigated multiferroics
    properties of certain thin films at Spectrum Labratories, Rio Piedras campus. Coauthored
    a \href{http://jap.aip.org/resource/1/japiau/v105/i8/p084110_s1?isAuthorized=no}{scientific
    paper} describing work completed. }{Oct 2008}{Dec 2008}

\buff

\Entry{\href{https://www.daad.org/}{daad} intern}{University of
M"unster}{Operated tomographic atom probe,
    transmission electron microscope, and field ion microscope at
    the Institue for Material \mbox{Physics}. Investigated effect of extreme temperatures on the rate of diffusion of
nano-materials.}{May 2008}{Sep 2008}
\fbuff


\MySection{Skills, Interests \& Expertise}
\buff

\Entry{Computer Languages}{}{Proficient in Python, R, Javascript
(\href{http://d3js.org/}{D3}), SVG. Familiar with HTML, CSS, MySQL, SQLite. Exposure to
Clojure, Haskell.
\href{https://github.com/scikit-learn/scikit-learn/commits?author=AWinterman}{Contributor}
to \href{http://scikit-learn.org/dev/}{Scikit-Learn}, a machine learning
toolkit.}{}{} 

\buff
\Entry{Relevant Coursework}{}{
    \textit{OHSU}: Biostatistics, Epidemiology. \newline
    \textit{Reed College}: 
    Mathematical Statistics,
    Probability,
    Abstract \&  \mbox{Linear}  Algebra,
    %Real \& Complex Analysis,
    Advanced Topics in Epistemology: Computation.
    %Topics in Algebra: Galois Theory  
    }
{}{}
\buff

\Entry{Interests}{}{\textit{Languages}: Fluent in Spanish. Intermediate German.
    \newline
    \textit{Hobbies}: Cooking, drawing (pencil, pen \& ink wash, charcoal),
    Ultimate Frisbee. Craft coffee and microbrews.}{}{}
\fbuff

\MySection{Community Involvement}
\buff

\Entry{Student \newline Leader}{Reed College}{Led four day backpack in Mt. Adams
    wilderness area for incoming Reed College freshmen. Responsibilities
include group safety, organizing meals, clean water, tending group
morale.}{Aug 2010}{}

\buff

\Entry{Organizer}{Jump Rope Club}{Student Health: Installed jump ropes in lobby
    of Reed College library to combat stress culture, encouraging students to
exercise as a study break.}{Feb 2009}{Apr 2009}

\buff

\Entry{Teacher}{Voz Workers' Rights Project}{Taught English to Latin
American adult day laborers. Focused on
vocabulary, pronunciation.}{Oct 2009}{}

\buff

\Entry{Volunteer}{Ayuda Directa}{Constructed dust-free building in remote
    Andean village to properly house government issued computers. Tutored
English vocabulary and grammar.}{Aug 2007}{}
\end{document}
