\documentclass[11pt]{letter}

\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\usepackage{fancyhdr}
%\usepackage[document]{ragged2e}
\usepackage[german]{babel}
\usepackage[top=1in, bottom=1in, right=1in, left=1in, footskip=16pt]{geometry}

%\usepackage[compact]{titlesec}
\usepackage{changepage}


\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{soul}


\pagestyle{fancy}

\fancyhead{}

\renewcommand{\headrulewidth}{1pt}

\usepackage{hyperref}
\hypersetup{
            colorlinks=true,
            urlcolor=steelblue,
            linkcolor=steelblue
}

\usepackage{color}
\definecolor{steelblue}{rgb}{0.02638, 0.5, 0.67578125}

\date{}
\chead{
    \textsc{\huge{\so{andrew winterman}}}
}
\cfoot{ 
    \hrule  \\
    \vspace{3px}
    2807 NE Glisan Apt. 304, Portland, OR 97232 \\
andywinterman@gmail.com - 714 362 6823 - 
\url{https://github.com/AWinterman}
}


\begin{document}


\begin{letter}{Twitter, Inc. \\
1355 Market St, Suite 900
 \hfill \today \\
San Francisco, CA 94103\\ 
}
\address{}

\begin{adjustwidth}{1in}{1in}

    \opening{To whom it may concern:}

    \thispagestyle{fancy}
I am applying for the Data Scientist position at Twitter on the strength of my
past experience and the suggestion of Lennon Day-Reynolds, a fellow Reed
College alumnus. I am excited by this opportunity to employ predictive
statistics and machine learning to Twitter's rich and varied data set.

I have experience at a boutique web development company prototyping data
visualization methods, doing data analysis, and implementing machine learning
algorithms for social media data. I do the full process, from data retrieval to
processing to constructing working prototypes of visualizations. I make scale
models of the finely polished product we push out the door. My data has, for
the most part, been small enough for my aging IMac to handle it, but I have run
large computations on Amazon's Elastic Cloud Compute, and written map-reduce
jobs for the Elastic MapReduce web service.

 Sharp and calm, I am a goal-oriented team player, eager to contribute. I am
 detail oriented, patient, and a quick study. I look forward to discussing my
 background and the Data Scientist position at Twitter, either over the phone
 or in person.

\closing{
Thank you, \\
Andrew Winterman}


\end{adjustwidth}


\end{letter}


\end{document}
