%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin,line]{resume}
\usepackage[german]{babel}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Andrew Winterman}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}


    3811 SE Ellis,                           \hfill  mobile: (714) 362-6823          \vspace{0mm}\\\vspace{0mm}%
    Portland, OR 97202                         \hfill     e-mail: andywinterman@gmail.com      \vspace{0mm}\\%
  \vspace{-4.5mm}%

    %__________________________________________________________________________________________________________________
    % Research Interests
 \section{\mysidestyle{Summary}} Energetic, communicative, recent graduate looking for employment.%__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

\textbf{Reed College}: B.A. in Mathematics; Thesis in statistics.
 \vspace{1mm} \hfill Aug 2006 - Dec 2010 \vspace{1mm}\\
\textbf{Deutsche Sommerschule am Pazifik}:  Language Immersion (German) \vspace{1mm} \hfill Summer 2009
\vspace{1mm} \\
\textbf{Universidad Belgrano}: Language Immersion (Spanish) \vspace{1mm} \hfill Summer 2006 \vspace{1mm}

    % Employment History
    \section{\mysidestyle Scientific\\Employment} 
\textbf{Research Experience for Undergraduates} \hfill  Intern \\ 
\textbf{at Reed College} \ \  \hfill Summer 2010 \\
Repaired and improved available statistical tools for cDNA microarray analysis. Worked with a team of undergraduates under Professors Susan Renn and Albyn Jones, developed statistical test of equivalence for use with microarray data. \\
\vspace{-2mm} \\
%\textbf{ Internal Research Grant} \hfill Assistant  \\ 
%\textbf{Reed College} \hfill Summer 2009 \vspace{0mm}	\\
%Researched combinatorics with Prof. V. Rao Potluri.
%\\\vspace{-2mm}\\
\textbf{Researcher at University of Puerto Rico,} \hfill  Intern\\
\textbf{Rio Piedras, Spectrum Laboratories} \hfill Fall 2008	\\
Executed a complicated scientific procedure to exacting standards. Coauthored N. M. Murari, R. Thomas, A. Winterman, R. E. Melgarejo, S. P. Pavunny, and R. S. Katiyar. ``Structural, electrical, and magnetic properties of chemical solution deposited Bi(Fe$_{0.95}$Cr$_{0.05}$)O$_3$ thin films on platinized silicon substrates," J. Appl Physics 105, 084110 (2009). 
\\\vspace{-2mm}\\
\textbf{Westf"alische Wilhelms-Universit"at M"unster and the} \hfill  Intern \\
\textbf{German Academic Exchange Service (DAAD)} \hfill Summer 2008	\\
Operated a tomographic atom probe, transmission electron microscope, and a field ion microscope. \\ Executed delicate scientific procedure designed to test the effect of extreme temperatures on the rate of diffusion of nano-materials.

\section{\mysidestyle Student Organizations }

\textbf{Outdoor Odyssey} \hfill Student Leader \\
\textbf{Orientation Trip} \hfill Summer 2010 \\
Led four day backpack in Mt. Adams wilderness area for incoming Reed College freshmen. Responsibilities include group safety, organizing meals, clean water, tending group moral.
\\\vspace{-2mm}\\
\textbf{Jump Rope} \hfill Organizer
\\\textbf{Club}  \hfill Spring 2009\\
Student Health: Installed jump ropes in lobby of Reed College library to combat stress culture, encourage students to exercise as a study break. 



	\section{\mysidestyle Language \& Construction \\ Employment}
\textbf{VOZ Workers' Rights}  \hfill Volunteer \\ \textbf{Education Project} \hfill Fall 2009 \\ Taught English to Latin American adult day laborers while they waited for employment. \\
\vspace{-2mm}\\    
\textbf{Ayuda} \hfill Volunteer \\    
\textbf{Directa} \hfill Summer 2007	\\
Constructed ``dust free" building in remote Andean village to properly house government issued computers. Tutored more advanced Quechua students in English vocabulary and grammar.    


%_________________________________________________________________________________________________________________
    % Programming
    \section{\mysidestyle Computer\\Skills}
 R: A language and environment for statistical computing, \\ \LaTeXe,  Java.
    %__________________________________________________________________________________________________________________
    % T
    \section{\mysidestyle Languages}
English (Fluent) \\
Spanish (Advanced)\\
German (Intermediate)   %__________________________________________________________________________________________________________________

    % Interests
\newpage
    \section{\mysidestyle Interests} 

Ultimate Frisbee (member of college team, 2006 - 2010) \\
Cooking, Tango \& Jazz, Commuting by bike \\
Traveling, Piano \& Percussion \\




    %__________________________________________________________________________________________________________________
    % Referees
%    \section{\mysidestyle Referees} 
%    {\sl Available on request.}



%______________________________________________________________________________________________________________________
\section{\mysidestyle References} 

\begin{tabular}{@{}p{6cm}p{6cm}}
\textbf{Professor Albyn Jones}       &  \textbf{Professor Suzy Renn}                   \\
Professor of Statistics                              &  Assistant Professor                       \\
Reed College                     &  Reed College                 \\
Portland, OR           &  Portland OR        \\
phone: 503 517 7518    &  phone: \textsl{available on request}     \\
e-mail: jones@reed.edu   &  e-mail: renns@reed.edu    \\
\end{tabular}

%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Dr Conrad Sanderson}            &  \textbf{Mr Sean Loye}                    \\
%Researcher                              &  Systems Engineer                         \\
%National ICT Australia                  &  Hewlett Packard                          \\
%St Lucia, Queensland, Australia         &  Milton, Queensland, Australia            \\
%phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
%e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
%\end{tabular}



%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

